---
title: "p8105_hw5_kz2411"
author: "Keming Zhang"
date: "11/14/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 8,
                      fig.asp = .8,
                      out.width = "80%"
                      )
library(tidyverse)
library(rvest)
library(broom)
library(naniar)
```

## Problem 1

```{r load data}
#load data
homicide_data_raw <- read_csv("data/homicide-data.csv", na = c("","unknown"))
```

The raw data has `r nrow(homicide_data_raw)` observations. There are `r ncol(homicide_data_raw)` variables, and they are `r colnames(homicide_data_raw)`. Their types are numeric or character.


```{r clean and group}
#clean and group
homicide_data_process <- homicide_data_raw %>%
  mutate(
    city_state = paste(city,state,sep = ", ")
  )

#total number of homicides and the number of unsolved homicides 
homicide_unsolved <- homicide_data_process %>%
  group_by(city_state) %>%
  #calculate number of homicides
  summarize(
    homicide_num = n(),
    disposition = disposition
  ) %>%
  filter(disposition %in% c("Closed without arrest","Open/No arrest")) %>%
  group_by(city_state) %>%
  #calculate number of unsolved homicides
  summarize(
    homicide_num = homicide_num,
    unsolved_num = n()
  ) %>%
  distinct()

homicide_unsolved
```


```{r prop.test}
#prop.test on Baltimore, MD
baltimore_data <- homicide_unsolved %>%
  filter(city_state == "Baltimore, MD")
baltimore_prop_test <- prop.test(pull(baltimore_data,unsolved_num),pull(baltimore_data,homicide_num))
tidy(baltimore_prop_test)
```

```{r prop.test map}
#calculate interval for all cities
city_prop_data <- homicide_unsolved %>%
  mutate(
    prop_test = map2(unsolved_num, homicide_num, prop.test),
    prop_test = map(prop_test, tidy)
  ) %>%
  unnest(cols = prop_test) %>%
  select(city_state,estimate,conf.low,conf.high)

city_prop_data
```

```{r plot city}
#plot for city
city_plot <- city_prop_data %>%
  arrange(estimate) %>%
  #order by estimate
  ggplot(aes(x = fct_reorder(city_state,estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "The estimates and CIs for each city",
    x = "City",
    y = "Estimate"
  ) +
  theme(axis.text.x = element_text(angle = 270, hjust = 0))

city_plot
```
Richmond has the lowest estimate and Chicago has the highest estimate and is apparently higher than any other city.

## Problem 2
```{r file list}
#file list
data_path <- "data/problem2_data"
file_list = list.files(data_path) %>%
  data.frame()
colnames(file_list) <- c("file")
```

```{r load file}
#load file and save reuslt to combine_data
combine_data <- file_list %>%
  mutate(
    complete_file = paste(data_path,file,sep = '/'),
    file_contents = map(complete_file,read_csv)
  ) %>%
  unnest(cols = file_contents) %>%
  select(file,week_1:week_8)
```

```{r clean data}
#tidy combine_data
#rename column
colnames(combine_data)[1] <- c("group_id")

#clean data and rename group_id
data_clean <- combine_data %>%
  janitor::clean_names() %>%
  mutate(
    group_id = gsub("con","control",group_id),
    group_id = gsub("exp","experimental",group_id),
    group_id = gsub(".csv","",group_id)
  ) %>%
  separate(group_id,c("group","subject_id"),sep = '_')
data_clean
```

```{r plot spaghetti}
plot_data <- data_clean %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_"
  ) %>%
  mutate(
    group_id = paste(group,subject_id, sep = " ")
  )

spaghetti_plot <- plot_data %>%
  ggplot(aes(x = week, y = observation, color = group_id, group = group_id)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Spaghetti plot for different groups",
    color = "Group-Subject ID"
  )

spaghetti_plot
```

From the plot, we can see that those from the experimental arm have higher observations than those form the control arm during week 8. And observations of those from the experimental arm increase over time, while observations of those from the control arm fluctuate up and down.

## Problem 3
```{r}
#load data
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing

#checking missing
miss_var_summary(iris_with_missing) %>% knitr::kable(digits = 3)
```

```{r fill missing}
#fill missing function
fill_missing = function(x) {
  #numeric variables
  if (is.numeric(x)) {
    x = ifelse(is.na(x),mean(x,na.rm = TRUE), x)
  }
  #character variables
  else if (is.character(x)) {
    x = ifelse(is.na(x),"virginica",x)
  }
}

#map fill_missing function
iris_no_missing <- map_dfr(iris_with_missing,fill_missing)
iris_no_missing

#checking no missing
miss_var_summary(iris_no_missing) %>% knitr::kable(digits = 3)
```

